Scheduling and Vectorization for MPC

### 2022-04-12 overleaf/paper_SIMD.tex
Small math mode paper fix

Next, the algorithm refines array MUX statements.
MPC-source after Cytron's SSA may result in statements $\texttt{A}_j = \emph{MUX}(..., \texttt{A}_k, \texttt{A}_l)$, which imply that any index
of A can be written at this point and therefore there is a loop-carried dependency. In some cases the MUX can be refined to just a single
index or a pair of indices, e.g., $\texttt{A}_j[i] = \emph{MUX}(c, \texttt{A}_k[i], \texttt{A}_l[i])$.

>>>>

Next, the algorithm refines array MUX statements.
MPC-source after Cytron's SSA may result in statements $\texttt{A}_j = \emph{MUX}(..., \texttt{A}_k, \texttt{A}_l)$, which imply that any index
of $A$ can be written at this point and therefore there is a loop-carried dependency. In some cases the MUX can be refined to just a single
index or a pair of indices, e.g., $\texttt{A}_j[i] = \emph{MUX}(c, \texttt{A}_k[i], \texttt{A}_l[i])$.
